Real-Time Systems

### 2013-10-02 beamer/dit-paper-presentation.tex
more beamer tentative change of nofpdit graph definition

\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{pgfpages}

@@

\begin{frame}
	\tableofcontents
\end{frame}

@@

\begin{frame}
    \tableofcontents[currentsection]
\end{frame}

@@

@@

        For given values of $a_i$, equation~(\ref{eq:FPDIT}) has one solution modulo $H$ if the following condition is respected:
        \[
            a_i + O_i \equiv a_j + O_j \; (\operatorname{mod} \; \operatorname{gcd}(T_i,
            T_j)) \; \forall i,j
        \]

@@

	\begin{frame}{Existence and value}

@@

	\begin{frame}{Redundancy in asynchronous systems}
		[$t_d$, $t_d + H$] is a feasibility interval
	\end{frame}

\section{Numerical Example}

	\begin{frame}{Example}
		Table, OCDT, figure
	\end{frame}

>>>>

\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{pgfpages}
\usepackage{algorithm}
\usepackage[noend]{algorithmic}

@@

\begin{frame}
    \tableofcontents[hideothersubsections]
\end{frame}

@@

\begin{frame}
    \tableofcontents[currentsection, hideothersubsections]
\end{frame}

@@

    \begin{frame}
        \tableofcontents[currentsection, hideothersubsections]
    \end{frame}

@@

@@

    \begin{frame}{Finding the FPDIT - Chinese Remainder Theorem}
        For given values of $a_i$, equation~(\ref{eq:FPDIT}) has one solution modulo $H$ if the following condition is respected:
        \[
            a_i + O_i \equiv a_j + O_j \; (\operatorname{mod} \; \operatorname{gcd}(T_i,
            T_j)) \; \forall i,j
        \]

        ...
    \end{frame}

    \begin{frame}{Finding the FPDIT value}

        \begin{algorithm}[H]
            \caption{Gauss's CRP Algorithm}
            \label{alg:algoCRP}
            \begin{algorithmic}[1]
                \REQUIRE $C$ the set of constraint $c$  $\left( t_d \equiv x(c) \; (\operatorname{mod} \; p(c)) \right)$
                \REQUIRE $H$ the hyperperiod of the system
                \FORALL{$c \in C$}
                    \STATE $Mc \leftarrow \frac{H}{p(c)}$
                    \STATE $invMc \leftarrow Mc^{-1} \; (mod \; p(c))$
                    \STATE $e_c \leftarrow Mc \cdot invMc$
                \ENDFOR
                \RETURN $\sum\limits_{c \in C}{x(c) \cdot e_c} \; (mod \; H)$
            \end{algorithmic}
        \end{algorithm}

    \subsection{Frequency of existence}

    \begin{frame}{Frequency of existence of the FPDIT}

    \begin{columns}[c]
        \column{0.4\textwidth}

        Systems were generated by
        \begin{itemize}
            \item Generating O
            \item Generating T
            \item Generating D
        \end{itemize}

        \column{0.6\textwidth}
        \includegraphics[width=\textwidth]{figs/nofpdit_4.png}

    \end{columns}

@@

    \begin{frame}
    \tableofcontents[currentsection, hideothersubsections]
    \end{frame}

	\begin{frame}{Initial description}
		[$t_d$, $t_d + H$] is a feasibility interval
	\end{frame}

\section{Numerical Example}
	\begin{frame}{Example}
		Table, OCDT, figure
	\end{frame}
